A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-31 paper.tex
typo fixes

As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.  Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.  This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
\begin{equation}
\label{eq:4d_12_general_def}
\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
\end{equation}
To see this, we must verify that the expression $S_1$ occuring in the $Q_{st}$-twisted action functional agrees with the corresponding expression in the $Q_0 + sQ_2$-twisted action functional.  This follows from the fact that the only term proportional to $t(\chi^*-t\wt\chi^*)$ in the $Q_0 + tQ_1$-twisted action functional from equation \ref{4d_donaldson_susy_prop} is proportional to $\wt \chi^*$, and so vanishes after setting $\wt \chi^* = 0$.

>>>>

As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.  Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.  This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
\begin{equation}
\label{eq:4d_12_general_def}
\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
\end{equation}
To see this, we must verify that the expression $S_1$ occuring in the $Q_{st}$-twisted action functional agrees with the corresponding expression in the $Q_0 + sQ_2$-twisted action functional.  This follows from the fact that the only term proportional to $t(\chi^*-t\wt\chi^*)$ in the $Q_0 + tQ_1$-twisted action functional from equation \ref{4d_donaldson_susy_prop} is proportional to $\wt \chi^*$, and so vanishes after setting $\wt \chi^* = 0$.
